---
title: "Plotting Networks with ggplot"
author: "Daniel Kaplan"
date: "August 4, 2014"
output: html_document
---

```{r}
require(DCFdevel)
require(ggplot2)
require(dplyr)
require(igraph)
```

This is an attempt to provide a simple interface for drawing networks using `ggplot()`.  I'm trying to get `igraph` to do the layout, then let edge properties be set by ggplot.

### An example Network

These are connections among NCI60 cell types, using the correlation between probe expression.  They came from the `cellCor` data frame in `2013-08-03-DTK-103.Rmd`.

```{r}
CellEdges <- read.csv("nciNetwork.csv")
CellEdges <- select(CellEdges, corr=correlation, one=cellLine, two=otherCellLine)
```

## Find positions for the vertices

The user can hand off a dataframe `Pos` that specifies the name, x, and y position of each node.  If there is no such array, the `Edges` array will be used to extract the vertex names and assign them a position.

`Pos` must have only two columns.

For development purposes:
```{r}
SmallEdges <- head(select(CellEdges,one,two))
SmallNet <- graph.data.frame( SmallEdges )
```


```{r}
getGraphPos <- function( Edges, Pos=NULL ) {
  JustEdges <- Edges[,c(1,2)]
  origNames <- names(JustEdges)[1:2]
  names(JustEdges) <- c("FROM","TO")
  if ( is.null( Pos ) ) {
    # Construct the locations using igraph
    # make the graph
    Net <- graph.data.frame( JustEdges )
    where <- layout.fruchterman.reingold( Net )
    Pos <- data.frame( x = where[,1], y = where[,2] )
    Pos$name <- vertex.attributes( Net )$name
  }
  # add the position information to the 
  FROM <- inner_join( JustEdges["FROM"], select(Pos,FROM=name,x,y))
  TO <- inner_join( JustEdges["TO"], select(Pos,TO=name,xend=x,yend=y))
  FROM$Group <- 1:nrow(FROM)
  return( cbind(FROM,TO) )
}
```

Trying to make a dplyr style interface.  I want to have the dataframe, then the `from` and `to` variables identified.


Return an aes() or a geom_segment() that can be used with segments.
```{r}
testing <- function(.eges, from, to, 
                    .vertices=NULL, name, x, y, 
                    layout=layout.circle ){
  vars <- structure(as.list(match.call()[-1]), class = "uneval")
  if (missing(from) || missing(to))
    stop("Must provide 'from' and 'to' variable names.")
  From <- eval( vars$from, envir=.edges )
  To   <- eval(   vars$to, envir=.edges )
  Edges <- data.frame( from=From, to=To)
  if ( !is.null(.vertices) ) {
    if (missing(x) || missing(y))
      stop( "Must provide 'name', 'x' and 'y' variable names for vertices.")
    # User has specified the vertices together with x and/or y positions
    X <- eval( vars$x, envir=.vertices )
    Y <- eval( vars$y, envir=.vertices )
    Names <- eval( vars$name, envir=.vertices )
    Pos <- data.frame( from=Names, .x.start = Y, .y.start = Y )
  } else {
    # get the positions automatically
    Net <- graph.data.frame( JustEdges )
    where <- layout.fruchterman.reingold( Net )
    Pos <- data.frame( x = where[,1], y = where[,2] )
    Pos$name <- vertex.attributes( Net )$name
  }
  
  return(Edges)
}
```

```{r}
vertexPosition <- function(edges) {
  # where should the vertices be located.
  
  }
```
